### 2015-07-07 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: minor updates to hose stream report

\section{Background}
\label{sec:Background}

>>>>

\section{Background}
\label{sec:Background}
%http://www.tft.com/literature/library/files/bfa.pdf
Bill Nelson and Keith Royer strongly recommend that the rotation be clockwise as viewed from the nozzle operator’s position. From many experiments it was determined that a clockwise rotation is more effective than a counterclockwise rotation. They say that:
1. Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle.
Counterclockwise rotation does just the opposite.
2. Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation
produces steam with an inactive and lazy action.
3. A clockwise rotation produces a faster knockdown time.
